## Intro

What we have:

- 53 datasets of 53 times series data (may be duplicated)
- one LABEL dataset (raw)

```{r}
list.files("dataset/1501")
```

## Output

Following the design of experiment (DOE), we define the outcome and our objectives

### Outcome

Since the LABEL dataset is the result of checking semi-products' quality criterias such as:

```{r}
df <- openxlsx::read.xlsx("dataset/labels.xlsx", sheet = "Sheet2", detectDates = FALSE)
colnames(df)
```

Quality criterias such as `AD`, `Vis`, `pH`, `SG` with quite enough data can be used as dependent variables for the thesis

### Objectives

We have already identified the target. The next task is to state the objectives.

Some options are

- Predict the value of quality critierias, or the `regression` problem
- Predict whether the batch is qualified, or the `binary classification` problem
- Predict which level of `goodness` the batch belongs to, or the `multi-label classification` problem

**Notes**:

1. Search scientific publication for these above terms: `regression`, `binary classification` and `multi-label classification`.
2. Some survey about the amount, advantages, dis-advantages of each type of problem in manufacturing industries.
3. Define levels of 'goodness' in industries and which papers used the same term.

The `Objective` of the thesis is stated below

1. Conduct a feature selection in which the chosen factor are decided by explainable methods such as statistics or SHAP value
2. Modeling the relationship between factors and outcomes to construct a decision - support application in which user will give inputs  and the models show the calculation and recommend the decision to make.
3. Build an web-based software that has a user interface for the decision-support application.
