I would like to express my sincere gratefulness to my supervisor, Assoc. Prof. Thoại Nam, for his enthusiastic guidance and continuous support during my research. 
Thanks to his broad knowledge and deep experience, his feedback has greatly increased my knowledge and scientific research skills.
The inspiring weekly catchups with him have encouraged me to push myself further and complete such challenging work.

I would like to show my all-hearted love for my family, Mom, Dad and my younger brother, for always being by my side along the journey.
Their warmness and cheerfulness significantly boosted my confidence and energy to continue working on the study. There is no time that they did not show me the pride they take in.

Special thanks to my love, Nhàn, for the empathy and emotional support she shows me all the time. They are so prestigious and invaluable to me and I heartfully appreciate them.

I also want to thank my supervisors and teammates, Mr. Nam, Huy, Quân, Trân, Mr. Điền, Mr. Quý, Mr. Tâm, Mr Thọ and Khôi, in the companies, both previous and current, for providing me the opportunity to balance the time spent on daily work and the research, especially, 
Mr. Quý and Mr. Điền to help me with the industrial expertise and experience,
Hiếu for suggesting I try out the SHAP, and Quỳnh for helping me organize my thesis and providing proofreading.

Finally, I want to thank all my family members and friends who are looking forward to my completion of this study and show me all the love.